---
title: "Simple R Notebook"
output: html_notebook
---

<!-- When we want code to be evaluated, but not displayed we use echo = F -->
<!-- By default, R Markdown is evaluated in a fresh R environment, so we have to
load our libraries at the start.  We will also discuss other ways of evaluating 
R Markdown where you can provide an environment -->
```{r, echo = F}

library(data.table)

```

#### You can very easily load in data and print out the summary
```{r}

data(mtcars)

DT <- as.data.table(mtcars)

DT[, summary(mpg)]

```

#### You can embed plots or other images
<!-- Note that you can use the fig.align option to change the alignment of the image -->
```{r, echo = F, fig.align = 'center'}
sink('/dev/null')
DT[, plot(x = hp, 
          y = mpg, 
          main = 'HP vs MPG', 
          xlab = 'Horsepower', 
          ylab = 'Miles Per Gallon')]
sink()
```

#### In case you want to use python you can do that too. Not sure why you wouldn't just use Jupyter.
```{python}
x = [1, 2, 3]

x.append(4)

print x

```

#### Problem 1: Create a code chunk below showing how to calculate the median mpg without actually evaluating the expression [Helpful guide](http://yihui.name/knitr/options/)
```{r}
# Your code goes here

```

#### Problem 2: Make this plot smaller (right now the default is 7x5)
```{r, echo = F, fig.align = 'center'}
sink('/dev/null')
DT[, plot(x = wt, 
          y = mpg, 
          main = 'Weight vs MPG', 
          xlab = 'Weight', 
          ylab = 'Miles Per Gallon')]
sink()
```
